[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper and references update

# Results {#sec-results}

## Opposite-Sex Religious Ceremony Type
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustype
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England, Roman Catholic, Other Christian Denominations, and Other Relgion Ceremonies Conducted Between 1970 and 2020 in England and Wales for Opposite-Sex Couples

>>>>

# Results {#sec-results}
Looking at the graphed data and summary statistics, there appears to be a clear decline in the number of opposite-sex couples opting for a religious ceremony across a fifty-year timeframe between 1970 and 2020. For same-sex couples, civil ceremonies have consistently and overwhelmingly been the most popular ceremony type since the legalization of same-sex marriage in 2014. The latter phenomenon is likely best explained by the relationship between religion and homophobia. Barbara Finlay and Carol S. Walter’s work in *Review of Religious Research* found that Protestants had the highest homophobia scores followed by Catholics, other Christian denominations, and other religions [@homophobiaresearch]. As same-sex religious ceremonies are conducted and approved by each religious authority [@statsguide], it could be possible that religious leaders do not approve of same-sex marriages. Another reason for the lack of same-sex religious ceremonies could also be non-heterosexual individuals moving away from religiosity due to conflicts between religious thought and their sexual identities.

## Opposite-Sex Religious Ceremony Type
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustype
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Blue), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 1970 and 2020 in England and Wales for Opposite-Sex Couples
